Cybersecurity is too important to be left to the specialists \\(Abstract 20 January, Paper 27th)

### 2019-01-16 ITiCSE2019.tex
Text around Java; conclusions

\subsection{Informal Resources}
The web abounds with informal resources: tutorials and code snippets. How good are these, and how good are people at using these? This has been looked at by \cite{Unruhetal2017a}, who took the top five results from Google for six queries. Of these 30 tutorials, 6 had SQL injection weaknesses, and 3 had Cross-Site Scripting\footnote{Number 7 in WASP's Top Ten \cite{OWASP2017a}.} weaknesses. Searching for these fragments in PHP projects GitHub found 82 instances of these fragments, of which 117 were verified by manual to be vulnerable --- 80\% of which were vulnerable to SQL injection.

\cite{Mengetal2018a,Chenetal2019a,Zorz2019a}

@@

>>>>

\subsection{Informal Resources}\label{sec:informal}
The web abounds with informal resources: tutorials and code snippets. How good are these, and how good are people at using these? This has been looked at by \cite{Unruhetal2017a}, who took the top five results from Google for six queries. Of these 30 tutorials, 6 had SQL injection weaknesses, and 3 had Cross-Site Scripting\footnote{Number 7 in OWASP's Top Ten \cite{OWASP2017a}.} weaknesses. Searching for these fragments in PHP projects on GitHub found 82 instances of these fragments, of which 117 were verified by manual to be vulnerable --- 80\% of which were vulnerable to SQL injection.

\subsection{The case of Java}\label{sec:Java}
To the best of the authors' knowledge, no survey equivalent to \cite{Drop2019} has been done for Java textbooks. Indeed, many such books go nowhere near security applications.  But this means that the programmer who has to implement security is left to the documentation of the package/API being used, and to informal resuorces. \cite{Mengetal2018a} analysed 503 CyberSecurity-related postings on the popular Stack overflow (\url{https://stackoverflow.com}) resource.  53\% were about the Spring Security framework (\url{https://projects.spring.io/spring-security/}), dominated by authentication (45\%). The discussion \cite[\S4.3.1]{Mengetal2018a} of cross-site request forgery (CSRF) is especially worrying.  By default, Spring implcitly enables protection against this. But all the accepted answers to CSRF-related failures simply suggested disabling they check. There were no negative comments about this, and indeed a typical response is ``Adding \verb!csrf().disable()!
solved the issue!!! I have no idea why it was enabled by default''.

\cite{Chenetal2019a,Zorz2019a}

@@

\section{Conclusions}

We have the following recommendations.
\begin{enumerate}
\item Database courses should look carefully at the security aspects of the texts they use, and the examples they quote, on the lines of \cite{Drop2019}.
\item All CS courses houdl emphasise that informal resources should come with a ``security health warning'': see sections \ref{sec:informal} and \ref{sec:Java}.
\end{enumerate}
